---
title: 'VIMC diagnostic report: site'
output:
  html_document: 
    theme: united
    highlight: tango
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(scene)
library(ggpubr)
library(data.table)

site<- site_data
# source plotting code for report
source('diagnostic_functions.R', local= knir::knit_global())


```

## VIMC site-level diagnostic report

This is a diagnostic report for VIMC outputs for `r site_name`, `r ur`. The EIR for this site is `r site_data$eir$eir[[1]]`. The description for this model run is `r description`. The scenario ran was `r scenario`. The population size of this model run was `r population`. The burn-in time was `r burnin` years. For this run, quick_run was `r quick_run` .

Cases averted per 100,000 fully vaccinated in this site up to 2040 = `r formatC(key_outcomes$cases_averted[grep("2040",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`

Cases averted per 100,000 fully vaccinated in this site up to 2100 = `r formatC(key_outcomes$cases_averted[grep("2100",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`

Deaths averted per 100,000 fully vaccinated in this site up to 2100 = `r formatC(key_outcomes$deaths_averted[grep("2100",key_outcomes$timeframe)], format="f", big.mark=",", digits=0)`.

Total cases averted in this site over all years in the model are: `r formatC(pull_tot_cases_averted(processed_output)[[1]]$cases_averted, format="f", big.mark=",", digits=0)` and total deaths averted: `r formatC(pull_tot_cases_averted(processed_output)[[1]]$deaths_averted, format="f", big.mark=",", digits=0)`

Total cases in the country in WMR 2020 were `r formatC(site_data$cases_deaths$wmr_cases[which(site_data$cases_deaths$year==2020)], format="f", big.mark=",", digits=0)`.

## Vaccine coverage specified for scenario

```{r inputs}

plot_vaccine_coverage(model_input)
intvns<- data.table::data.table(model_input$interventions)

intro_yr<- min(intvns[rtss_coverage!= 0 | r21_coverage!= 0, year])


ints<- melt(model_input$interventions, id.vars = 'year', measure.vars = c("itn_use", "itn_input_dist", "tx_cov", "smc_cov", "pmc_cov", "irs_cov", "rtss_cov"))

ggplot(data= ints)+
  geom_line(mapping = aes(x= year, y= value, color= variable))+
  labs(color= 'Intervention',
       y= 'Proportional coverage value',
       x=' Year',
       title = 'Intervention coverage over simulation period') +
  plotting_theme
```

# Doses delivered in raw model outputs

```{r doses}
plot_doses_delivered(raw_output)


```

# Site file diagnostics

# Site file inputs

```{r prevalence, echo=FALSE}

prevalence_diagnostic(site)


```

# Model outputs

```{r}
plot_pfpr_over_time(raw_output, intro_yr = intro_yr)
```

## Site file

```{r pop, echo=FALSE}

population_diagnostic(site)


```

## Modelled outputs

```{r population, echo=FALSE, fig.height=10, fig.width= 15}

population_diagnostic_model(agg_output, pg= 1, intro_yr = intro_yr, summary = T)


population_diagnostic_model(processed_output, pg= 1, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 2, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 3, intro_yr = intro_yr)
population_diagnostic_model(processed_output, pg= 4, intro_yr = intro_yr)


```

# Incident cases

```{r incident cases, echo=FALSE, fig.height=10, fig.width= 15}

incident_cases_diagnostic(agg_output, pg= 3, intro_yr = intro_yr, summary = T)

incident_cases_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incident_cases_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)


```

# Incidence rate

```{r incidence rate, echo = FALSE, fig.height=10, fig.width= 10}

incidence_rate_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)
  
incidence_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
incidence_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Deaths

```{r deaths, echo=FALSE, fig.height=10, fig.width= 15}

mortality_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)


mortality_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# Mortality rate

```{r mort rate, echo=FALSE, fig.height=10, fig.width= 15}
  mortality_rate_diagnostic(agg_output, pg= 1, intro_yr = intro_yr, summary = T)


mortality_rate_diagnostic(processed_output, pg= 1, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 2, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 3, intro_yr = intro_yr)
mortality_rate_diagnostic(processed_output, pg= 4, intro_yr = intro_yr)

```

# DALYs

```{r dalys, echo = FALSE, fig.height=10, fig.width= 15}
daly_diagnostic(agg_output, pg = 1, intro_yr = intro_yr, summary = T)

daly_diagnostic(processed_output, pg = 1, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 2, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 3, intro_yr = intro_yr)
daly_diagnostic(processed_output, pg = 4, intro_yr = intro_yr)

```

# Cases averted by age

```{r cases averted, echo =FALSE, fig.height=10, fig.width= 15}
plot_cases_averted(processed_output)

```
